{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Small correction

	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases have, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper. For the sake of keeping the notation reasonably concise, we will still keep this notation. However, by convention, this shall mean using a B-spline basis consisting of $L$ functions from this point on.

>>>>

	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper. For the sake of keeping the notation reasonably concise, we will still keep this notation. However, by convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.
